---
title: "spatial_Patterns_ABMTheorico"
author: "Andres Baeza"
date: "October 3, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

In this file we read results from the abm2.
The first two plots, plot 1 and plot 2 illustrate the distance metric. Plots 3 and 4 the state of infrastructure.
```{r}
require(ggplot2)
require(RColorBrewer)
require(png)
require(grid)
require(sensitivity)
require(ggtern)
require(fmsb)
require(gridExtra)
```

## Including Plots

You can also embed plots, for example:

```{r}
A100<-as.data.frame(matrix(ncol=16,nrow=10000))
B100<-as.data.frame(matrix(ncol=16,nrow=10000))
C100<-as.data.frame(matrix(ncol=16,nrow=10000))

A300<-as.data.frame(matrix(ncol=16,nrow=10000))
B300<-as.data.frame(matrix(ncol=16,nrow=10000))
C300<-as.data.frame(matrix(ncol=16,nrow=10000))

A600<-as.data.frame(matrix(ncol=16,nrow=10000))
B600<-as.data.frame(matrix(ncol=16,nrow=10000))
C600<-as.data.frame(matrix(ncol=16,nrow=10000))

colnames(A100)<-c("xcor","ycor","district_here","Infra_S_here" ,"Infra_F_here","altitude","socialpressureTOTAL_S" ,"socialpressureTOTAL_F","total_exposure_S","total_exposure_F", "infra_S_age","infra_F_age","d_m_F","d_n_F","d_m_S","d_n_S")

colnames(A100)<-colnames(A100)
colnames(B100)<-colnames(A100)
colnames(C100)<-colnames(A100)

colnames(A300)<-colnames(A100)
colnames(B300)<-colnames(A100)
colnames(C300)<-colnames(A100)

colnames(A600)<-colnames(A100)
colnames(B600)<-colnames(A100)
colnames(C600)<-colnames(A100)



A100_MH<-scan(file = '/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/100-0-300-2000-spatialpatterns.txt')
B100_MH<-scan(file = '/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/100-0-300-2001-spatialpatterns.txt')
C100_MH<-scan(file = '/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/100-0-300-2002-spatialpatterns.txt')



A300_MH<-scan(file = '/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/300-0-300-2000-spatialpatterns.txt')
B300_MH<-scan(file = '/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/300-0-300-2001-spatialpatterns.txt')
C300_MH<-scan(file = '/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/300-0-300-2002-spatialpatterns.txt')

A600_MH<-scan(file = '/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/600-0-300-2000-spatialpatterns.txt')
B600_MH<-scan(file = '/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/600-0-300-2001-spatialpatterns.txt')
C600_MH<-scan(file = '/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/600-0-300-2002-spatialpatterns.txt')

count = 0
for (i in 1:10000){
  for (j in 1 :16){
   count = count + 1
  # A50[i,j]<-A50_MH[count]
  # B50[i,j]<-B50_MH[count]
  # C50[i,j]<-C50_MH[count]

   A100[i,j]<-A100_MH[count]
  B100[i,j]<-B100_MH[count]
  C100[i,j]<-C100_MH[count]
  
  A300[i,j]<-A300_MH[count]
  B300[i,j]<-B300_MH[count]
  C300[i,j]<-C300_MH[count]

  A600[i,j]<-A600_MH[count]
  B600[i,j]<-B600_MH[count]
  C600[i,j]<-C600_MH[count]
  }
}

#2036-1-Increase Infra Coverage-spatialpatterns_i


```



```{r}
lim_d=c(0,max(A600$d_m_S,B600$d_m_S,C600$d_m_S))
# d_C50<-ggplot(data=subset(C50,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = ""Squeaky wheel" ",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")
# 
# d_B50<-ggplot(data=subset(B50,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "Repair first" ,y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")
# 
# d_A50<-ggplot(data=subset(A50,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "Expand access",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")



d_C100<-ggplot(data=subset(C100,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")
d_B100<-ggplot(data=subset(B100,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")

d_A100<-ggplot(data=subset(A100,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")


d_C300<-ggplot(data=subset(C300,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")
d_B300<-ggplot(data=subset(B300,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")

d_A300<-ggplot(data=subset(A300,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")





d_C600<-ggplot(data=subset(C600,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")

d_B600<-ggplot(data=subset(B600,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")


d_A600<-ggplot(data=subset(A600,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")

png(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/SP_dist_S_ro0tau300.png",width = 10,height = 12,res=900,units = "in")
title1=textGrob("Distance Metric", gp=gpar(fontface="bold",fontsize=20))
title2=textGrob("Time", gp=gpar(fontface="bold",fontsize=30))
grid.arrange(d_C100,d_B100,d_A100,
             d_C300,d_B300,d_A300,
             d_C600,d_B600,d_A600,ncol=3,top=title1,left=title2)

dev.off()
```

#flooding
```{r}
lim_d=c(0,max(A300$d_m_F,B300$d_m_F,C300$d_m_F))

d_C100<-ggplot(data=subset(C100,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")
d_B100<-ggplot(data=subset(B100,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")

d_A100<-ggplot(data=subset(A100,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")


d_C300<-ggplot(data=subset(C300,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")
d_B300<-ggplot(data=subset(B300,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")

d_A300<-ggplot(data=subset(A300,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_S))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")

d_C600<-ggplot(data=subset(C600,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_F))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")
d_B600<-ggplot(data=subset(B600,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_F))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")


d_A600<-ggplot(data=subset(A600,district_here ==1),aes(x=xcor,y=ycor,fill=d_m_F))+geom_tile()+coord_equal()+ scale_fill_gradient("Vulnerability",low = "lightgreen",high = "red",limits=lim_d,guide = "none",na.value = "red")+labs(title = "",y="",x="")+theme(text = element_text(size=20),panel.background = element_rect(fill="black", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+ geom_contour(aes(z=altitude),bins = 10,colour="black")

png(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/SP_dist_F_ro0tau300.png",width = 12,height = 18,res=300,units = "in")
title1=textGrob("policy scenario", gp=gpar(fontface="bold",fontsize=30))
title2=textGrob("Time", gp=gpar(fontface="bold",fontsize=30))
grid.arrange(d_C100,d_B100,d_A100,
             d_C300,d_B300,d_A300,
             d_C600,d_B600,d_A600,ncol=3,top=title1,left=title2)

dev.off()
```

```{r}
C100$infra_S_age[which(C100$Infra_S_here==0)]<-(-9)
C100$infra_F_age[which(C100$Infra_F_here==0)]<-(-9)


C300$infra_S_age[which(C300$Infra_S_here==0)]<-(-9)
C300$infra_F_age[which(C300$Infra_F_here==0)]<-(-9)

C600$infra_S_age[which(C600$Infra_S_here==0)]<-(-9)
C600$infra_F_age[which(C600$Infra_F_here==0)]<-(-9)


B100$infra_S_age[which(B100$Infra_S_here==0)]<-(-9)
B100$infra_F_age[which(B100$Infra_F_here==0)]<-(-9)


B300$infra_S_age[which(B300$Infra_S_here==0)]<-(-9)
B300$infra_F_age[which(B300$Infra_F_here==0)]<-(-9)

B600$infra_S_age[which(B600$Infra_S_here==0)]<-(-9)
B600$infra_F_age[which(B600$Infra_F_here==0)]<-(-9)



A100$infra_S_age[which(A100$Infra_S_here==0)]<-(-9)
A100$infra_F_age[which(A100$Infra_F_here==0)]<-(-9)


A300$infra_S_age[which(A300$Infra_S_here==0)]<-(-9)
A300$infra_F_age[which(A300$Infra_F_here==0)]<-(-9)

A600$infra_S_age[which(A600$Infra_S_here==0)]<-(-9)
A600$infra_F_age[which(A600$Infra_F_here==0)]<-(-9)



```


#create cutoffs for plotting age infra
```{r}
C100<-transform(C100, z.age_S=cut(C100$infra_S_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels = c("No urban","no infrastructure","New","Mature","Old","Very old")))
C100<-transform(C100, z.age_F=cut(C100$infra_F_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
C300<-transform(C300, z.age_S=cut(C300$infra_S_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
C300<-transform(C300, z.age_F=cut(C300$infra_F_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
C600<-transform(C600, z.age_S=cut(C600$infra_S_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
C600<-transform(C600, z.age_F=cut(C600$infra_F_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))


B100<-transform(B100, z.age_S=cut(B100$infra_S_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
B100<-transform(B100, z.age_F=cut(B100$infra_F_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
B300<-transform(B300, z.age_S=cut(B300$infra_S_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
B300<-transform(B300, z.age_F=cut(B300$infra_F_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
B600<-transform(B600, z.age_S=cut(B600$infra_S_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
B600<-transform(B600, z.age_F=cut(B600$infra_F_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))

A100<-transform(A100, z.age_S=cut(A100$infra_S_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
A100<-transform(A100, z.age_F=cut(A100$infra_F_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
A300<-transform(A300, z.age_S=cut(A300$infra_S_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
A300<-transform(A300, z.age_F=cut(A300$infra_F_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
A600<-transform(A600, z.age_S=cut(A600$infra_S_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))
A600<-transform(A600, z.age_F=cut(A600$infra_F_age, breaks=c(-30,-10,0.1,100,200,300,1000),labels =c("No urban","no infrastructure","New","Mature","Old","Very old")))



#colors1 <- colorRampPalette(c("#66CDAA","#F0F8FF","#CDC0B0","#838B8B","#000000"))(length(levels(C100$z.age_S)))
colors1 <- colorRampPalette(c("lightgreen","grey","cadetblue1","dodgerblue4","darkorange","darkred"))(length(levels(C100$z.age_S)))
```



#Figure 3: Condition of infrastructure system over time and space

```{r}


IS_C100<-ggplot(data=subset(C100,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(C100$z.age_S)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =5,colour="black")


IS_B100<-ggplot(data=subset(B100,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B100$z.age_S)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =5,colour="black")

IS_A100<-ggplot(data=subset(A100,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(A100$z.age_S)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =5,colour="black")





IS_C300<-ggplot(data=subset(C300,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(C300$z.age_S)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =5,colour="black")


IS_B300<-ggplot(data=subset(B300,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B300$z.age_S)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =5,colour="black")

IS_A300<-ggplot(data=subset(A300,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(A300$z.age_S)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =5,colour="black")


IS_C600<-ggplot(data=subset(C600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(C600$z.age_S)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =5,colour="black")


IS_B600<-ggplot(data=subset(B600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B600$z.age_S)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =5,colour="black")

IS_A600<-ggplot(data=subset(A600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(A600$z.age_S)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =5,colour="black")


png(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/SP_InfraS_ro0tau300.png",width = 18,height = 18,res=300,units = "in")
title1=textGrob("Age and extent of potable water Infrastructure", gp=gpar(fontface="bold",fontsize=20))
title2=textGrob("Time", gp=gpar(fontface="bold",fontsize=20))
grid.arrange(IS_C100,IS_B100,IS_A100,
             IS_C300,IS_B300,IS_A300,
             IS_C600,IS_B600,IS_A600,ncol=3,top=title1,left=editGrob(title2,rot=90))

dev.off()

png(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/SP_InfraS_ro0tau300finaltime.png",width = 15,height = 5,res=900,units = "in")
title1=textGrob("Age and extent of potable water Infrastructure", gp=gpar(fontface="bold",fontsize=20))
title2=textGrob("Time", gp=gpar(fontface="bold",fontsize=20))
grid.arrange(IS_C600,IS_B600,IS_A600,ncol=3,top=title1,left=editGrob(title2,rot=90))

dev.off()

```

#Figure 4: Condition of sewer infrastructure system over time and spape

```{r}


IF_C100<-ggplot(data=subset(C100,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(C100$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins =10,colour="black")


IF_B100<-ggplot(data=subset(B100,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B100$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins = 10,colour="black")

IF_A100<-ggplot(data=subset(A100,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  coord_equal()+
  geom_tile()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(A100$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins = 10,colour="black")





IF_C300<-ggplot(data=subset(C300,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(C300$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins = 10,colour="black")


IF_B300<-ggplot(data=subset(B300,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B300$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins = 10,colour="black")

IF_A300<-ggplot(data=subset(A300,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(A300$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins = 10,colour="black")





IF_C600<-ggplot(data=subset(C600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(C600$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins = 10,colour="black")


IF_B600<-ggplot(data=subset(B600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B600$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins = 10,colour="black")

IF_A600<-ggplot(data=subset(A600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(A600$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  theme(text = element_text(size=20),panel.background = element_rect(fill="lightgreen", colour="black"),panel.grid.major =  element_blank(),panel.grid.minor = element_blank() )+
  geom_contour(aes(z=altitude),bins = 10,colour="black")


png(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/SP_infraF_ro0tau300.png",width = 18,height = 18,res=300,units = "in")
title1=textGrob("Age and extent of sewer Infrastructure", gp=gpar(fontface="bold",fontsize=20))
title2=textGrob("Time", gp=gpar(fontface="bold",fontsize=20))
grid.arrange(IF_C100,IF_B100,IF_A100,
             IF_C300,IF_B300,IF_A300,
             IF_C600,IF_B600,IF_A600,ncol=3,top=title1,left=editGrob(title2,rot=90))

dev.off()

png(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/ABM_V2/landscape_pics/SP_infraF_ro0tau300finaltime.png",width = 15,height = 5,res=900,units = "in")
title1=textGrob("Age and extent of sewer Infrastructure", gp=gpar(fontface="bold",fontsize=20))
title2=textGrob("Time", gp=gpar(fontface="bold",fontsize=20))
grid.arrange(IF_C600,IF_B600,IF_A600,ncol=3,top=title1,left=editGrob(title2,rot=90))

dev.off()

grid.arrange(IF_C600,IF_B600,IF_A600,ncol=3,top=title1,left=editGrob(title2,rot=90))

```

## figure 2 paper: Spatial patterns of age in both infrastructure systems 
```{r,fig.height=10,fig.width=15}

IS_C600<-ggplot(data=subset(C600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(C600$z.age_S)),guide="none")+
  labs(title = "Squeaky wheel",y="Potable water system",x="")+
  geom_contour(aes(z=altitude),bins =5,colour="black")+
  theme(text = element_text(size=15),
        plot.title=element_text(size=20),
        panel.background = element_rect(fill="lightgreen", colour="black"),
        panel.grid.major =  element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin=unit(c(0,0,0,0), "cm"))


IS_B600<-ggplot(data=subset(B600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B600$z.age_S)),guide="none")+
  labs(title = "Repair first",y="",x="")+
  geom_contour(aes(z=altitude),bins =10,colour="black")+
  theme(text = element_text(size=15),
        plot.title=element_text(size=20),
        panel.background = element_rect(fill="lightgreen", colour="black"),
        panel.grid.major =  element_blank(),
        panel.grid.minor = element_blank() ,
        plot.margin=unit(c(0,0,0,0), "cm"))

IS_A600<-ggplot(data=subset(A600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_S))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(A600$z.age_S)),guide="none")+
  labs(title = "Expand access",y="",x="")+
  geom_contour(aes(z=altitude),bins =10,colour="black")+
  theme(text = element_text(size=15),
        plot.title=element_text(size=20),
        panel.background = element_rect(fill="lightgreen", colour="black"),
        panel.grid.major =  element_blank(),
        panel.grid.minor = element_blank() ,
        plot.margin=unit(c(0,0,0,0), "cm"))

IF_C600<-ggplot(data=subset(C600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
    geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B600$z.age_F)),guide="none")+
  labs(title = "",y="Sewer system",x="")+
  geom_contour(aes(z=altitude),bins = 10,colour="black")+
  theme(text = element_text(size=15),
        panel.background = element_rect(fill="lightgreen", colour="black"),
        panel.grid.major =  element_blank(),
        panel.grid.minor = element_blank() ,
        plot.margin=unit(c(0,0,0,0), "cm"))


IF_B600<-ggplot(data=subset(B600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
  geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B600$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  geom_contour(aes(z=altitude),bins = 10,colour="black")+
  theme(text = element_text(size=15),
        panel.background = element_rect(fill="lightgreen", colour="black"),
        panel.grid.major =  element_blank(),
        panel.grid.minor = element_blank() ,
        plot.margin=unit(c(0,0,0,0), "cm"))

IF_A600<-ggplot(data=subset(A600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
    geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B600$z.age_F)),guide="none")+
  labs(title = "",y="",x="")+
  geom_contour(aes(z=altitude),bins = 10,colour="black")+
  theme(text = element_text(size=15),
        panel.background = element_rect(fill="lightgreen", colour="black"),
        panel.grid.major =  element_blank(),
        panel.grid.minor = element_blank() ,
        plot.margin=unit(c(0,0,0,0), "cm"))


title1=textGrob("Policy", gp=gpar(fontface="bold",fontsize=20))
title2=textGrob("System", gp=gpar(fontface="bold",fontsize=20))

png(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/abm2/Files_publication_ABM1/Figure2_spatialpatterns_ro0tau300.png",width = 15,height = 10,res=300,units = "in")

grid.arrange(
  IS_C600,IS_B600,IS_A600,
  IF_C600,IF_B600,IF_A600,ncol=3,top=title1,left=editGrob(title2,rot=90))

dev.off()
grid.arrange(
  IS_C600,IS_B600,IS_A600,
  IF_C600,IF_B600,IF_A600,ncol=3,top=title1,left=editGrob(title2,rot=90))


legend_pl<-ggplot(data=subset(A600,district_here==1),aes(x=xcor,y=ycor,fill=z.age_F))+
    geom_tile()+
  coord_equal()+
  scale_fill_manual(name="Vulnerability",values=setNames(colors1, levels(B600$z.age_F)))+
  labs(title = "",y="",x="")+
  geom_contour(aes(z=altitude),bins = 10,colour="black")+
  theme(text = element_text(size=10),
        panel.background = element_rect(fill="lightgreen", colour="black"),
        panel.grid.major =  element_blank(),
        panel.grid.minor = element_blank() )

png(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/abm2/Files_publication_ABM1/Legend_Figure2_spatialpatterns_ro0tau300.png",width = 5,height = 5,res=300,units = "in")
legend_pl
dev.off()
```
